Assessing spatial patterning of Middle Paleolithic human settlement in Western Iberia

### 2020-10-15 analysis/paper/paper.Rmd
install rstudio 1.3

---
title: "Assessing spatial patterning of Middle Paleolithic human settlement in Western Iberia"
author:
  - João Cascalheira
  - Célia Gonçalves
  - Daniela Maio
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  Middle Paleolithic; GIS; Western Iberia
---

@@

#library(MidPalSet) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory

@@

# Extract values from stack for each site within a 20 m radius
sites_vals <- raster::extract(terrainstack,
                      sites_sub_long,
                      buffer = 20,
                      fun = mean,
                      sp = TRUE)

>>>>

---
title: "Assessing spatial patterning of Middle Paleolithic human settlement in Western Iberia"
author:
  - João Cascalheira
  - Célia Gonçalves
  - Daniela Maio
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  Middle Paleolithic; Settlement patterns; GIS; Western Iberia
---

@@

#library(MidPalSet) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` directory

@@

# Extract mean values from stack for each site and all caves within a 20 m radius
sites_vals <- raster::extract(terrainstack,
                      sites_sub_long,
                      buffer = 20,
                      fun = mean,
                      sp = TRUE)

caves_vals <- raster::extract(terrainstack,
                              caves_long,
                              buffer = 20,
                              fun = mean,
                              sp = TRUE)
